How cryptic is cryptic diversity? \newline Machine learning approaches to fine scale variation in the morphology of \textit{Emys marmorata}.

### 2013-06-17 documents/turtle_presentation.Rnw
most plots at final stage

\section{Results}
\begin{frame}[fragile]
  \frametitle{Results: mophometrics}
<<gm, results = 'hide', fig.width = 3.5, fig.height = 3.5, eval = TRUE>>=
morph <- ggpairs(turtle.adult, columns = c(1:3),
                 upper = 'blank',
                 params = c(LabelSize = 2, gridLabelSize = 2, size = 1))
fits <- procGPA(turtle.land.adult)
land <- mshape.plot(fits)
land <- land + coord_equal()
morph <- putPlot(morph, land, 1, 3)
morph
@

@@

\begin{frame}
  \frametitle{Generalize using best random forest model}
<<>>=
oo <- Reduce(cbind, Map(function(x) x$t, rr))
colnames(oo) <- groups
dd <- melt(oo)
gdist <- ggplot(dd, aes(x = value, fill = X2)) + geom_density(alpha = 0.3)
gdist <- gdist + theme(legend.title = element_blank(),
                       legend.margin = unit(0, 'cm'),
                       legend.text = element_text(size = 5),
                       axis.title = element_text(size = 8),
                       axis.text = element_text(size = 5))
gdist <- gdist + scale_fill_manual(name = '', values = cbp)

@@

\begin{frame}
  \frametitle{Best classification scheme via RF model results}
<<>>=
gg <- class.map(adult.train$spinks, adult.test$spinks, labs$spinks, 
                trf.a.analysis$class$spinks$pred, map)
gg <- gg + scale_colour_manual(name = '', values = cbp)
gg <- gg + theme(#legend.position = 'none',
                 legend.margin = unit(0, 'cm'),
                 legend.text = element_text(size = 5),
                 axis.title = element_text(size = 8),
                 axis.text = element_text(size = 5))
gg
@

@@

<<fig.width = 3.75, fig.height = 3.75>>=
# get mean of each class
spi <- turtle.adult$spinks
wspi <- lapply(levels(spi), function(x, y) which(y == x), y = spi)
mspi <- lapply(wspi, function(x, y) mshape(y[, , x]), y = turtle.land.adult)
par(mfrow = c(2, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
mins <- lapply(mspi, function(x) min(x[, 2]))
mins <- min(unlist(mins))
mapply(function(x, m, n) {
      #tpsgrid(x, m, mag = 2, ext = 0, cex = 2)
      plotRefToTarget(M1 = m, M2 = x, mag = 2)
      title(main = paste(n))}, x = mspi, n = levels(spi),
      MoreArgs = list(m = mt), SIMPLIFY = FALSE)
par(mfrow = c(1, 1))
@

@@

<<fig.width = 5>>=
mt <- mshape(turtle.land.adult)

@@

par(mfrow = c(1, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
tpsgrid(turtle.land.adult[, , fst.min], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , fst.min])
title(main = 'min observed')
tpsgrid(turtle.land.adult[, , fst.max], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , fst.max])
title(main = 'max observed')
par(mfrow = c(1, 1))
@

@@

\begin{frame}
  \frametitle{Shape across PC8}
<<fig.width = 5>>=
par(mfrow = c(1, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
tpsgrid(turtle.land.adult[, , snd.min], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , snd.min])
title(main = 'min observed')
tpsgrid(turtle.land.adult[, , snd.max], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , snd.max])
title(main = 'max observed')
par(mfrow = c(1, 1))
@
\end{frame}

@@

\begin{frame}
  \frametitle{Acknowledgements}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item Ben Frable, Dallas Krentzel, Michael Foote, David Bapst
        \item COLLECTIONS
        \item FUNDING AGENCIES
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[height = 0.25\textheight, keepaspectratio = true]{figure/chicago} \\
      \includegraphics[height = 0.25\textheight, width = \textwidth, keepaspectratio = true]{figure/field} \\
      \includegraphics[height = 0.25\textheight, keepaspectratio = true]{figure/csu}
    \end{column}
  \end{columns}
\end{frame}
\end{document}

>>>>

\section{Results}
\begin{frame}[fragile]
  \frametitle{Results: mophometrics}
<<gm, results = 'hide', fig.width = 3.5, fig.height = 3.5, eval = TRUE>>=
morph <- ggpairs(turtle.adult, columns = c(1:3),
                 upper = 'blank',
                 params = c(LabelSize = 2, gridLabelSize = 2, size = 1))
fits <- procGPA(turtle.land.adult)
links <- c(1:7, 13:8)
land <- mshape.plot(fits, links = links)
land <- land + coord_equal()
morph <- putPlot(morph, land, 1, 3)
morph
@

@@

\begin{frame}
  \frametitle{Generalize using best random forest model}
<<>>=
oo <- Reduce(cbind, Map(function(x) x$t, rr))
colnames(oo) <- groups
dd <- melt(oo)
gdist <- ggplot(dd, aes(x = value, fill = X2)) + geom_density(alpha = 0.5,
                                                              size = 0.1)
gdist <- gdist + theme(legend.position = 'none',
                       #legend.title = element_blank(),
                       #legend.margin = unit(0, 'cm'),
                       #legend.text = element_blank(),
                       axis.title = element_text(size = 8),
                       axis.text = element_text(size = 5))
gdist <- gdist + scale_fill_manual(name = '', values = cbp)

@@

\begin{frame}
  \frametitle{Best classification scheme via RF model results}
<<>>=
gg <- class.map(adult.train$spinks, adult.test$spinks, labs$spinks, 
                trf.a.analysis$class$spinks$pred, map)
gg <- gg + scale_colour_manual(name = '', values = cbp)
gg <- gg + theme(legend.position = 'none',
                 #legend.margin = unit(0, 'cm'),
                 #legend.text = element_text(size = 5),
                 axis.title = element_text(size = 8),
                 axis.text = element_text(size = 5))
gg
@

@@

<<fig.width = 3.75, fig.height = 3.75>>=
# get mean of each class

mt <- mshape(turtle.land.adult)

spi <- turtle.adult$spinks
wspi <- lapply(levels(spi), function(x, y) which(y == x), y = spi)
mspi <- lapply(wspi, function(x, y) mshape(y[, , x]), y = turtle.land.adult)
par(mfrow = c(2, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
mins <- lapply(mspi, function(x) min(x[, 2]))
mins <- min(unlist(mins))
lmat <- cbind(links, c(links[-1], links[1]))
mapply(function(x, m, n) {
      #tpsgrid(x, m, mag = 2, ext = 0, cex = 2)
      plotRefToTarget(M1 = m, M2 = x, mag = 2, links = lmat)
      title(main = paste(n))}, x = mspi, n = levels(spi),
      MoreArgs = list(m = mt), SIMPLIFY = FALSE)
par(mfrow = c(1, 1))

multi.mean <- multishape.plot(mspi, links = links)
@

@@

<<fig.width = 5>>=

@@

#par(mfrow = c(1, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
#    xaxt = 'n', yaxt = 'n', bty = 'n')
#tpsgrid(turtle.land.adult[, , fst.min], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , fst.min])
#title(main = 'min observed')
#tpsgrid(turtle.land.adult[, , fst.max], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , fst.max])
#title(main = 'max observed')
#par(mfrow = c(1, 1))

ex.lab <- function(var, value) {
  value <- as.character(value)
  if(var == 'lab') {
    value[value == '1'] <- 'min'
    value[value == '2'] <- 'max'
  }
  return(value)
}

fst.mean <- multishape.plot(list(turtle.land.adult[, , fst.min], 
                                 turtle.land.adult[, , fst.max]), 
                            links = links,
                            labeller = ex.lab)
fst.mean <- fst.mean + theme(axis.title = element_blank(),
                             axis.text = element_text(size = 5))
fst.mean
@

@@

\begin{frame}
  \frametitle{Shape across PC8}
<<fig.width = 5>>=
#par(mfrow = c(1, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
#    xaxt = 'n', yaxt = 'n', bty = 'n')
#tpsgrid(turtle.land.adult[, , snd.min], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , snd.min])
#title(main = 'min observed')
#tpsgrid(turtle.land.adult[, , snd.max], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , snd.max])
#title(main = 'max observed')
#par(mfrow = c(1, 1))

snd.mean <- multishape.plot(list(turtle.land.adult[, , snd.min], 
                                 turtle.land.adult[, , snd.max]), 
                            links = links,
                            labeller = ex.lab)
snd.mean <- snd.mean + theme(axis.title = element_blank(),
                             axis.text = element_text(size = 5))
snd.mean
@
\end{frame}

@@

\begin{frame}
  \frametitle{Acknowledgements}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item Ben Frable, Dallas Krentzel, Michael Foote, David Bapst
        \item collections at CAS, FMNH, LACM, LSUMNS, MSE, MVZ, NMNH, SBMNH, SDMNH, UCMP, UMZC
        \item NSF DBI-0306158 to KDA
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[height = 0.25\textheight, keepaspectratio = true]{figure/chicago} \\
      \includegraphics[height = 0.25\textheight, width = \textwidth, keepaspectratio = true]{figure/field} \\
      \includegraphics[height = 0.25\textheight, keepaspectratio = true]{figure/csu}
    \end{column}
  \end{columns}
\end{frame}
\end{document}
